The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L445

\subsection{Timescales}
In order to map a dynamical state to a final alignment (e.g. librating orbit $\mapsto$ polar alignment), we are required to assume that the disk lifetime $t_\text{disk}$ is longer than the disk evolution timescale $t_\text{evol}$. The evolution timescale is the characteristic decay time for a disk whose inclination has been perturbed from a stable point (e.g., polar or coplanar), and while it is described by \citet{lubow2018} in their equation (29), it is only known up to a constant of proportionality:
\begin{equation}
    \label{eq:tevol}
    t_\text{evol} \propto \frac{h^2}{\alpha f^2(1-f)^2 e_\text{b}^2(1+4e_\text{b}^2) \Omega_\text{b}} ,
\end{equation}
where $h\equiv H/r$ is the disk aspect ratio, $f\equiv M_2/M$ is the mass ratio, and $\Omega_\text{b}$ is the binary orbital frequency.

>>>>

\subsection{Timescales}
In order to map a dynamical state to a final alignment (e.g. librating orbit $\mapsto$ polar alignment), we are required to assume that the disk lifetime $t_\text{disk}$ is longer than the disk evolution timescale $t_\text{evol}$. The evolution timescale is the characteristic decay time for a disk whose inclination has been perturbed from a stable point (e.g., polar or coplanar), and while it is described by \citet{lubow2018} in their equation (29), it is only known up to a constant of proportionality:
\begin{equation}
    \label{eq:tevol}
    t_\text{evol} \propto \frac{h^2}{\alpha f^2(1-f)^2 e_\text{b}^2(1+4e_\text{b}^2) \Omega_\text{b}} ,
\end{equation}
where $h\equiv H/r$ is the disk aspect ratio, \RR{$f\equiv M_2/M_\text{b}$ is the mass ratio between the secondary star and the total binary mass}, and $\Omega_\text{b}$ is the binary orbital frequency.
